Are parental care induced gene expression patterns affect more by internal cues or external stimuli?

### 2019-09-07 docs/manipulation_manuscript.Rmd
looking better
now with new fig

---
title: Are parental care induced gene expression patterns affect more by internal cues or external stimuli?
author:
  - name: Rayna M Harris
    email: rmharris@ucdavis
    affiliation: UC Davis
    corresponding: "rmharris@ucdavis"
  - name: Suzanne Austin
    affiliation: UC Davis
  - name: Andrew Lang
    affiliation: UNH
  - name: Matthew MacManes
    affiliation: UNH
  - name: Rebecca M Calisi
    affiliation: UC Davis           
address:
  - code: UC Davis
    address: UC Davis, Davis, CA
  - code: UNH
    address: UNH, smalltown, NH
abstract: |
  Are parental care induced gene expression patterns affect more by internal cues or external stimuli? We test two alternative hypothesis: internal clock cues versus external offspring stimuli by manipulating the timing of normal transitions during parental care. When we removed offpsring, we find the most pronounces chagnes in gene expression later during incubation or right after hatch, compared to early removeal of eggs. Given the similarity in gene expression the days immediately preceeding and immedately following hatch, we do not have the power to say weether gene expression patters are more like hatch or incuabtion when dummmy egg are used to extend incubation. This matters because...
author_summary: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

@@

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
library(cowplot)
ggdraw() + draw_image("../figures/manipulation/offspringremoval-1.png") 
```

>>>>

---
title: Are parental care induced gene expression patterns affect more by internal cues or external stimuli?
author:
  - name: Rayna M Harris
    email: rmharris@ucdavis
    affiliation: UC Davis
    corresponding: "rmharris@ucdavis"
  - name: Suzanne Austin
    affiliation: UC Davis
  - name: Andrew Lang
    affiliation: UNH
  - name: Matthew MacManes
    affiliation: UNH
  - name: Rebecca M Calisi
    affiliation: UC Davis           
address:
  - code: UC Davis
    address: UC Davis, Davis, CA
  - code: UNH
    address: UNH, smalltown, NH
abstract: |
  Are parental care induced gene expression patterns affect more by internal cues or external stimuli? We test two alternative hypothesis: internal clock cues versus external offspring stimuli by manipulating the timing of normal transitions during parental care. When we removed offpsring, we find the most pronounces chagnes in gene expression later during incubation or right after hatch, compared to early removeal of eggs. Given the similarity in gene expression the days immediately preceeding and immedately following hatch, we do not have the power to say weether gene expression patters are more like hatch or incuabtion when dummmy egg are used to extend incubation. This matters because...
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

@@

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5, fig.cap= "Circulating prolactin levels with an without manipulation."}
ggdraw() + draw_image("../figures/hormones/prolactin-manip-1.png") 
```

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5, fig.cap= "Offspring removal."}
ggdraw() + draw_image("../figures/manipulation/offspringremoval-1.png") 
```

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5, fig.cap = "Manipulation of timing of hatch with dummy eggs and foster chicks. "}
ggdraw() + draw_image("../figures/manipulation/prolongextend-1.png") 
```
